### 2018-04-30 paper/message-passing-design.tex
experiments and text

%\paragraph*{Header preparation}

@@

Once Alice get the \(H_\rdv\), Alice uses \([\Send]\) at some
later time to send the message to Bob using any of her devices from
its \squad.% (See \cref{SPORSend}). 
First, \([\Send]\) extends the route
\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \(\Send\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \(\Fwd\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful.% (See \cref{SPORFwd}). 
Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_\rdv = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).

>>>>

\begin{table}[t]
\resizebox{\columnwidth}{!}{
\begin{tabular}{lp{0.9\linewidth}}
\toprule
\multicolumn{2}{c}{\textbf{Parameters of the algorithm}} \\
\midrule
$\theta$ & Stopping criterion for the layers creation: maximum authorized  probability that all devices in a layer fail at once. \\
$L$      & Number of layers in a Predictive Onion Route. \\
$l = (L-1)/2$ & Number of layers (excluding $\LRV$) created by each end of the route. \\
\bottomrule
\end{tabular}
}
\label{tab:parameters}
\end{table}

\paragraph*{Header preparation} \commentAL{TODO}

@@

Once Alice get the \(H_\rdv\), Alice uses \(\Send\) at some
later time to send the message to Bob using any of her devices from
its \squad.% (See \cref{SPORSend}). 
First, \(\Send\) extends the route
\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \(\Send\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \(\Fwd\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful.% (See \cref{SPORFwd}). 
Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_\rdv = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).
